Seshadri constants of curve configurations on surfaces

### 2024-03-16 Response to reviewer.tex

\documentclass[12pt,twoside,reqno]{amsart}
%\documentclass[12pt]{article}

\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{amsthm, amsmath, amscd, amssymb,centernot}
\usepackage[all]{xy}
\usepackage[T1]{fontenc}
\usepackage[left=2.5cm,top=2.5cm,bottom=3cm,right=2.5cm]{geometry}
\usepackage{amsthm, amsmath, amscd, amssymb,centernot}
\usepackage{comment}
\setlength{\headheight}{15.2pt}
\setlength\parskip{.1in}
\setlength\parindent{0.2in}

%\usepackage{tikz}https://www.overleaf.com/project/642e283246ec4730b8bdf398
\usepackage{csquotes}

\newcommand{\s}{\varepsilon}

\numberwithin{equation}{section}
\newtheorem{theorem}{Theorem}[section]
\newtheorem*{theorem*}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{definition}
\newtheorem{question}[theorem]{Question}

\begin{document}
\title{Response to Reviewer}
\begin{description}
\item [Mauscript Number] IJM-D-22-00005 \\
\item [Full Title] Seshadri constants on some blow ups of Projective spaces
\end{description}

We start by thanking the anonymous referee for carefully reading the manuscript and suggesting 
useful changes and also for pointing out an error in the definition of ``\textit{multiplicity of a curve along a line in $\mathbb{P}^3$}''. We hope that after making these changes, the paper has becomes more accessible for the readers and its overall quality has improved considerably. We have made all the changes suggested by the referee and some other modifications, which we felt necessary. Following are the detailed (point by point) explanation of changes that we have made on the basis of the report. \\

We agree with the referee about the problem in our way of using the definition of multiplicity of an irreducible curve $C$ along a line $l$, both 
contained in $\mathbb{P}^3$. We have made it clear in the manuscript now that this is defined as the length of zero dimensional 
scheme $C \cap l \subset \mathbb{P}^3$, as pointed out by the referee. On the basis of this new (correct) definition, we have modified our arguments in theorems of Section $4$ and that of Section $5$. We now get some restricted results about Seshadri constants in case of $r=5,6$ line blow ups of $\mathbb{P}^3$ (Proposition 4.3), $r=4,5,6$ and $7$ line blow ups of $\mathbb{P}^4$ (Proposition 5.4) and $r=3,4$ and $5$ line blow ups of $\mathbb{P}^5$ (Remark 4).  In the cases not covered in the above list, we get bounds mainly. We give precise values of Seshadri constants only when points are special, for example (2), (3) and (4) of Theorem 4.2, (2), (3) of Theorem 5.3, and (2) of Theorem 5.5. However we do compute $\varepsilon(X_{r,0}^k,L)$ in various cases which appear in Remarks 1,2, and 5 and are explained towards the end of this letter.\\

\textbf{List of minor mathematical issues we fixed:}
\begin{enumerate}
 \item We have changed the arguments in page 3, line -2, as per referee's suggestions.  
 \item We have mentioned now in line -9 of page 4 that we use (2) to conclude the result. 
 \item We have set $m_i = 0$ for $i = s+1,..., 2n$ and moved $m_i + m_{i+n}$ after the summation on page 5, line 1-2. 
 \item We deleted the second $\sum\limits_{i=1}^s$ in the repetition. 
 \item We have added the missing case in the proof of Theorem 3.3 on page 5, line 12. 
 \item On page 6 line -2, we have added a precise reference namely ``\textit{from inequality (3) of Theorem 3.3}''. 
 \item We replaced $d>0$ with $d \geq 0$ in the statements of Theorem 4.1 (1), (2), (3) and also in the proof. 
 \item We replaced $d>0$ with $d \geq 0$ in the statements of Theorem 5.1 (1), (2), (3), Proposition 5.2 and also in the proofs. 
\end{enumerate}

\textbf{List of grammar issues/typos we fixed:}
\begin{enumerate}
 \item Rectified the spelling mistake in Demailly. 
 \item ``One of the very important'' has been changed to ``One of the most important'' page 1, line -11.
 \item We changed ``Seshadri constant can be'' to ``Seshadri constants can be'' on page 1, line -6.
 \item Done.
 \item We replaced the phrase ``d is large enough as in Proposition 3.2'' with ``d is large enough namely 
 $\sum_{i=1}^s m_i - nd \leq b_l$, where $b_l$ is as in Proposition 3.2''.
 \item We changed the notation $H_2$ by $H'$ on page 6, line -9. 
 \item Done.
 \item Does not exist in the modified version.
 \item Does not exist in the modified version.
 \item Does not exist in the modified version.
\end{enumerate}

\textbf{Some other small changes which we have done:} \\
Second part of the paper is rewritten to some extent. We give here the detailed account of changes that we have done from the previous version.
\begin{enumerate}
    \item We introduce some notations in the beginning of \textit{Section 4}, which we use in the proof of Theorem 4.2 and in later part of the paper. We have also added a paragraph before Theorem 4.2 where we explain ``the meaning of multiplicity of $C$ along a line $l$''. 
    \item After Theorem 4.2, we have added a \textit{Remark 1} where we compute $\varepsilon(X_{r,0}^3,L)$ for $r=1,...,4$.
    \item We then added a Proposition 4.3 giving some partial results about $\varepsilon(X_{r,0}^3,L)$ for $r=5$ and 
    a \textit{Remark 2} bounding $\varepsilon(X_{5,0}^3,L)$. We leave $r=6,7$ cases as the results in those cases are similar to Prop. 4.3 and Rem. 2.
    \item In section 5, we have added a paragraph before Theorem 5.3, where we introduce some notation about the intersection of joins of lines $J(l_i, l_j)$ and of $J(l_i, l_k)$.
    \item After Theorem 5.3, we added a \textit{Remark 3}, where we compute $\varepsilon(X_{4,0}^4,L,x)$ when $x \in l_j \cap J(l_i,l_k)$.
    \item We then added a Propostion 5.4, where we get partial result about $\varepsilon(X_{4,0}^4,L)$ (we again leave $r=5,6,7$ cases).
    \item We also note in \textit{Remark 4}, that similar results like Prop. 5.4 holds for $\varepsilon(X_{r,0}^5,L)$ 
    for $r=3,4,$ and $5$ (note that for $r=1,2$ we have Theorem 5.5).
    \item Finally in \textit{Remark 5}, we have added a note about the global Seshadri constant $\varepsilon(X_{r,0}^k,L)$ for $k=4,5$ and $r=1,...,7$, $r=1,...,5$ respectively.
\end{enumerate}

\end{document}

### 2024-03-16 Response/Response to reviewer.tex

%\usepackage{tikz}https://www.overleaf.com/project/642e283246ec4730b8bdf398
\usepackage{csquotes}

\newcommand{\s}{\varepsilon}

\numberwithin{equation}{section}
\newtheorem{theorem}{Theorem}[section]
\newtheorem*{theorem*}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{definition}
\newtheorem{question}[theorem]{Question}

\begin{document}
\title{Response to Reviewer}
\begin{description}
\item [Mauscript Number] GMJ 231005 \\
\item [Full Title] Seshadri Constants of Curve Configurations on Surfaces
\item [Author] Krishna Hanumanthu, Praveen Roy and Aditya Subramaniam
\end{description}

We start by thanking the anonymous referee for carefully reading the manuscript and suggesting 
useful changes and also for pointing out an error in the Assumption 2.1 and therefore the ambiguity in Theorem 2.5. We also agree with the reviewer that the example 2.21 is 
better to be shorten focusing only on the computation related to Seshadri constants. We have made all these changes, and we hope that after making these changes, the paper has becomes more accessible for the readers and its overall quality has improved considerably.  Following are the detailed (point by point) explanation of changes that we have made on the basis of the report. \\

We agree with the referee about the problem in our way of using the Assumption 2.1. While writing the paper, we always had in mind the \textbf{connectedness of the arrangement}, 
which we somehow missed to incorporate in the Assumption 2.1. We have made it clear in the manuscript now. Note that, now we don't require the semi-ampleness of divisor $A$ for $C_i^2$ to be positive, and it follows 
from the connectedness of the arrangement. Also, we would like to keep second assumption in Assumption 2.1, as removing that requires lot of new work and we aren't quite interested to carry out the required work, in that direction, 
as of now. The last concern of reviewer has also been addressed, we 
have updated the last example 2.21 and it has been shorten. \\

We once again thank the referee for a quick review, we hope that we addressed all the concern of the referee regarding this manuscript.

### 2024-03-16 Response/Response to reviewer.tex

\newcommand{\s}{\varepsilon}

\numberwithin{equation}{section}
\newtheorem{theorem}{Theorem}[section]
\newtheorem*{theorem*}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{definition}
\newtheorem{question}[theorem]{Question}

\begin{document}
\title{Response to Reviewer}
\begin{description}
\item [Mauscript Number] GMJ 231005 \\
\item [Full Title] Seshadri Constants of Curve Configurations on Surfaces
\item [Author] Krishna Hanumanthu, Praveen Roy and Aditya Subramaniam
\end{description}

We start by thanking the anonymous referee for carefully reading the manuscript and suggesting 
useful changes and also for pointing out an error in the Assumption 2.1 which lead to the ambiguity in Theorem 2.5. We also agree with the reviewer that the example 2.21 is 
better to be shorten focusing only on the computation related to Seshadri constants. We have made all these changes, and we hope that after making these changes, the paper has becomes more accessible for the readers and its overall quality has improved considerably.  Following are somewhat detailed explanation of changes that we have made on the basis of the report. \\

We agree with the referee about the problem in our way of using the Assumption 2.1. While writing the paper, we always had in mind the \textbf{connectedness of the arrangement}, 
which we somehow missed to incorporate in the Assumption 2.1. We have made it clear in the manuscript now. Note that, now we don't require the semi-ampleness of divisor $A$ for $C_i^2$ to be positive, and it follows 
from the connectedness of the arrangement. Additionally, we would prefer to retain the second part of Assumption 2.1, as removing that requires significant amount of additional work which we are currently not inclined to pursue.
 Regarding the reviewer's final concern, we have revised Example 2.21, shortening it to focus solely on the computation of the Seshadri constant. \\

### 2024-03-16 sc-curve-config.tex
Actual version submitted
Aditya informed that the previous version was not the one we submitted and this is the one.

\address{Indian Institute of Science Education and Research Tirupati, Rami Reddy Nagar, Karakambadi Road, Mangalam (P.O.)
Tirupati, Andhra Pradesh, INDIA – 517507.}

\email{adityasubramaniam@labs.iisertirupati.ac.in}
\subjclass[2020]{14C20,14N10, 14N20}

@@

	 Suppose that there exists an irreducible and reduced curve $D$, different from $C_{i}$ for $i \in \{1,\ldots, d\}$, having multiplicity $m_{p}(D)$ at each point $p \in \mathcal{P}$ such that
		$$\frac{L \cdot D}{\sum_{p \in \mathcal{P}} m_{p}(D)} < \frac{L\cdot C_1}{C_1^2(d-1)}.$$
This gives
		$$(\triangle) : \quad (L \cdot D)C_1^2(d-1) < \left(\sum_{p \in \mathcal{P}} m_{p}(D)\right)L\cdot C_1.$$
		By B\'ezout's theorem, we obtain
		\begin{eqnarray*}
		D\cdot (C_{1}+ \ldots + C_{d})=d(D\cdot C_1) &\geq& \sum_{p \in \mathcal{P}}m_{p}(D)\cdot m_{p}(C_{1}+ \ldots + C_{d})\\
		&\stackrel{(*)}{\geq}& 2\sum_{p \in \mathcal{P}} m_{p}(D) \\
		&\stackrel{(\triangle)}{>}& \frac{2(L \cdot D)C_1^2(d-1)}{L\cdot C_1},
		\end{eqnarray*}
		where $(*)$ comes from the fact that all the singular points of $C_{1}+ \ldots + C_{d}$ are at least double points. Now we use the nefness 
		of $\frac{dC_1^2}{(d-1)(L\cdot C_1)}L-C_1$ and note the following  inequality: 
		\[
		\frac{dC_1^2}{(d-1)(L\cdot C_1)}L\cdot D \geq D\cdot C_1.
		\] 
		This leads to the following:
		\begin{eqnarray*}
			\frac{d^2C_1^2}{(d-1)(L\cdot C_1)}L\cdot D &\geq& d (D\cdot C_1) > \frac{2(d-1)(L\cdot D)C_1^2}{L\cdot C_1} \\
			\Rightarrow \frac{d^2C_1^2}{d-1} &>& 2(d-1)C_1^2 \quad \quad \text{(since $L$ is ample)} \\
			\Rightarrow \left(\frac{d}{d-1} \right)^2 &>& 2 \quad \quad \text{(since $C_1^2 = C_1\cdot C_2 > 0$)}.
		\end{eqnarray*}
		This is a contradiction, since $d\geq 4$.
	\end{proof}
	\begin{corollary}
		\label{coro:star}
		If $\mathcal{C} = \{C_{1}, \ldots, C_{d}\}$ is a star configuration with $d \geq 4$  and $L$ is an ample line bundle on $X$ such that $ C_i \in |mL|$ for all $i$ and a positive integer $m>0$, then 
		$$\varepsilon(X, L,{\rm Sing}(\mathcal{C})) = \frac{1}{m(d-1)}.$$
	\end{corollary}

@@

		On the other hand, the configurational Seshadri constant is given by
		$$	\varepsilon_{\mathcal{C}_n'}(L)= \frac{3n(L\cdot C_1)}{f_1}= \frac{e+1}{e(n+1)}.$$
		Thus in this case, both these constants agree.

		Next, we considered a curve arrangement  $\mathcal{K}'$ on $X_e$ with $e > n$ which is a pullback of the Klein arrangement of lines $\mathcal{K} \subset \mathbb{P}^2.$ The curve arrangement  $\mathcal{K}'$ consists of 21 curves with $t_4=21e$ and $t_3=28e.$ Then by the choice of an ample line bundle $L$ on $X_e$ as in Example \ref{Hirz}, we obtained the following value of Seshadri constant 
		$$\varepsilon(X_e, L,{\rm Sing}(\mathcal{K}')) = \frac{e+1}{8e}.$$
		On the other hand, the configurational Seshadri constant is given by
		$$	\varepsilon_{\mathcal{K}'}(L)= \frac{21(L\cdot C_1)}{f_1}= \frac{e+1}{8e}.$$
		Thus in this case too both these constants agree.

@@

		On the other hand, the configurational Seshadri constant is given by
		$$	\varepsilon_{\mathcal{W}'}(L)= \frac{45(L\cdot C_1)}{f_1}= \frac{e+1}{16e}.$$
		Thus in this case too both the constants agree.

@@

>>>>

\address{Indian Institute of Science Education and Research Tirupati, Rami Reddy Nagar, Karakambadi Road, Mangalam (P.O.),
Tirupati, Andhra Pradesh, INDIA – 517507.}

\email{adityasubramaniam@labs.iisertirupati.ac.in}
\subjclass[2020]{14C20,14N10,14N20}

@@

	 Suppose that there exists an irreducible and reduced curve $D$, different from $C_{i}$ for $i \in \{1,\ldots, d\}$, having multiplicity $m_{p}(D)$ at each point $p \in \mathcal{P}$ such that
		$$\frac{L \cdot D}{\sum_{p \in \mathcal{P}} m_{p}(D)} < \frac{L\cdot C_1}{C_1^2(d-1)}.$$
This gives
		$$(\triangle) : \quad (L \cdot D)C_1^2(d-1) < \left(\sum_{p \in \mathcal{P}} m_{p}(D)\right)L\cdot C_1.$$
		By B\'ezout's theorem, we obtain
		\begin{eqnarray*}
		D\cdot (C_{1}+ \ldots + C_{d})=d(D\cdot C_1) &\geq& \sum_{p \in \mathcal{P}}m_{p}(D)\cdot m_{p}(C_{1}+ \ldots + C_{d})\\
		&\stackrel{(*)}{\geq}& 2\sum_{p \in \mathcal{P}} m_{p}(D) \\
		&\stackrel{(\triangle)}{>}& \frac{2(L \cdot D)C_1^2(d-1)}{L\cdot C_1},
		\end{eqnarray*}
		where $(*)$ comes from the fact that all the singular points of $C_{1}+ \ldots + C_{d}$ are at least double points. Now we use the nefness 
		of $\frac{dC_1^2}{(d-1)(L\cdot C_1)}L-C_1$ and note the following  inequality: 
		\[
		\frac{dC_1^2}{(d-1)(L\cdot C_1)}L\cdot D \geq D\cdot C_1.
		\] 
		This leads to the following:
		\begin{eqnarray*}
			\frac{d^2C_1^2}{(d-1)(L\cdot C_1)}L\cdot D &\geq& d (D\cdot C_1) > \frac{2(d-1)(L\cdot D)C_1^2}{L\cdot C_1} \\
			\Rightarrow \frac{d^2C_1^2}{d-1} &>& 2(d-1)C_1^2 \quad \quad \text{(since $L$ is ample)} \\
			\Rightarrow \left(\frac{d}{d-1} \right)^2 &>& 2 \quad \quad \text{(since $C_1^2 = C_1\cdot C_2 > 0$)}.
		\end{eqnarray*}
		This is a contradiction, since $d\geq 4$.
	\end{proof}
	\begin{corollary}
		\label{coro:star}
		If $\mathcal{C} = \{C_{1}, \ldots, C_{d}\}$ is a star configuration on a nonsingular projective surface $X$ with $d \geq 4$  and $L$ is an ample line bundle  on $X$ such that $ C_i \in |mL|$ for all $i$ and a positive integer $m>0$, then 
		$$\varepsilon(X, L,{\rm Sing}(\mathcal{C})) = \frac{1}{m(d-1)}.$$
	\end{corollary}

@@

		On the other hand, the configurational Seshadri constant is given by
		$$	\varepsilon_{\mathcal{C}_n'}(L)= \frac{3n(L\cdot C_1)}{f_1}= \frac{e+1}{e(n+1)}.$$
		Thus, in this case, both these constants agree.

		Next, we considered a curve arrangement  $\mathcal{K}'$ on $X_e$ with $e > n$ which is a pullback of the Klein arrangement of lines $\mathcal{K} \subset \mathbb{P}^2.$ The curve arrangement  $\mathcal{K}'$ consists of 21 curves with $t_4=21e$ and $t_3=28e.$ Then by the choice of an ample line bundle $L$ on $X_e$ as in Example \ref{Hirz}, we obtained the following value of Seshadri constant 
		$$\varepsilon(X_e, L,{\rm Sing}(\mathcal{K}')) = \frac{e+1}{8e}.$$
		On the other hand, the configurational Seshadri constant is given by
		$$	\varepsilon_{\mathcal{K}'}(L)= \frac{21(L\cdot C_1)}{f_1}= \frac{e+1}{8e}.$$
		Thus, in this case too, both the constants agree.

@@

		On the other hand, the configurational Seshadri constant is given by
		$$	\varepsilon_{\mathcal{W}'}(L)= \frac{45(L\cdot C_1)}{f_1}= \frac{e+1}{16e}.$$
		Thus, in this case too, both the constants agree.

@@

\subsection*{Declaration of interests}
The authors declare that they have no known competing financial interests or personal relationships
that could have appeared to influence the work reported in this paper.
